---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# controlcharts

<!-- badges: start -->
[![R-CMD-check](https://github.com/StatEcon1989/controlcharts/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/StatEcon1989/controlcharts/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/StatEcon1989/controlcharts/graph/badge.svg)](https://app.codecov.io/gh/StatEcon1989/controlcharts)
<!-- badges: end -->

CURRENTLY IN DEVELOPMENT:
Control charts allow real time testing for upwards and/or downwards shifts in a process without the need to wait for enough observations to apply tests for structural changes.
The package allows performing these control charts fast and efficiently by using C++.

## Installation

You can install the development version of controlcharts from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("StatEcon1989/controlcharts")
```

## Example

This is a basic example which shows how you could easily apply an EWMA control chart if your data is tabulated (this example requires data.table):

```{r example}
library(controlcharts)
# create the example data
T <- 500L # length of the time series
table <- data.table::data.table(X = rnorm(n = T, mean = 0.25), TIME = Sys.Date() + 1:T) # simulating the (out-of-control) data as table

# parametrization of the EWMA control chart
side <- "both"
lambda <- 0.1
ARL <- 250L

# calculate the critical value for the control limits of the EWMA chart
h <- calculate_control_limit_ewma(lambda = lambda, ARL = ARL, fir = TRUE, side = side,
                                  replications = 2000L)
# apply the EWMA and append the corresponding columns
table[, c("z", "upper_limit", "lower_limit", "exceedance") := ewma_cc(x = X, lambda = lambda, h = h, fir = TRUE, side = side)]
head(table)

# plot the control chart
table[, plot_ewma(.SD, dates = TIME)]
```
